\section{Introduction}

Meta Platforms Inc., also referred to in this paper as Meta and
formerly known as Facebook Inc., is an American transnational holding
company, which owns a technological conglomerate, based in Menlo Park,
California. It is a parent organization of Facebook, Instagram,
WhatsApp and Oculus. Being one of the most valuable companies in the
world, it is also one of the Big Tech companies in U.S. information
technology, alongside Amazon, Google, Apple and Microsoft. The company
makes nearly all profit from selling advertising space in their
services. Since its foundation Meta followed the objective of bringing
people together and make them able to communicate easily. In the last
decade more and more people started using it, to the point that it
became the massive corporation it is today. however, some problems
have emerged in the last decade, since the amount of tdata it had to
handle became so big. Hate speech (HS) is one of them: content that
incites to violence and rage, tagetting minorities and people based on
their etnicity. Consumers are activerly aware of the issue, as
evidenced by the growing number of people opting out of the platforms
for reasons related to HS \cite{art:fortuna2018survey}. At the same
time, building systems that can contrast this phenomena is really
difficult and requires a big quantity of resouces and skill. Meta on
its side started contrasting HS in 2016, starting a journey in AI that
lead it to became an AI superpower, alongside other tech gigantes,
such as Google, Microsoft and Amazon. The technology has not yet
showed its limits, and indeed, starts to be more and more adopted by
the people for everyday tasks, so that more and more data can be
collected to make it better.

There is still much uncertainty about the direction of this technology
and what the innovations in this fileds will bring us, as research
about the inner dynamics of AI usage is still scare.

What might still be uncertain, is how the the use of this technology
for the battle against HS is in Meta's interests. We'll see why this
is the case.
